### 2014-12-04 fundamentals/examples.tex
adding DRE acronym
remove TODO

The \Class{BatchReactor} archetype from \Cycamore has the ability to accept
fuel materials from an arbitrary number of different sources, delineated by
commodity. Custom, non-uniform preferences can be set for each different fuel
commodity.  The dynamic resource exchange \TODO{acro or not?} enables a reactor to
preferentially accept recycled \gls{MOX} fuel over fresh \gls{UOX} fuel.  In this
simulation, the
\Class{BatchReactor} was configured to run with a 3 batch core on 18 month cycles and
a 2-month refueling period.  Adjusting and setting parameters such as these is
as simple as editing numbers in an input file such as:

@@

Figure \ref{fig:puseries1} shows the full-system plutonium buildup for open
(no recycle), modified open, and closed (infinite-pass recycle) \TODO{whats
the diff btw closed and the multi-pass from above? It's referred to as fully
closed multi-pass recycle, which is a bit confusing.} variations of
the scenario described above (all just a single reactor).  The figure was
generated directly from \Cyclus output data. After several batch cycles (near
month 300 \TODO{here and below: month or time step?}) in the modified open and closed cases, enough separated fissile
material accumulates in the fuel fabrication facility to generate a full
recycled batch.  When this batch is transmuted, more plutonium is burned than
created.  This results in a drop in the total fuel cycle system plutonium
inventory.  This pattern repeats roughly every 10 cycles (200 months) for the
modified open case and every 9 cycles (180 months) for the closed case.
Because the modified open scenario does not re-recycle material, it takes the
fabrication facility 1 cycle longer to accumulate a full batch of
fissile material.

>>>>

The \Class{BatchReactor} archetype from \Cycamore has the ability to accept
fuel materials from an arbitrary number of different sources, delineated by
commodity. Custom, non-uniform preferences can be set for each different fuel
commodity.  The \gls{DRE} enables a reactor to
preferentially accept recycled \gls{MOX} fuel over fresh \gls{UOX} fuel.  In this
simulation, the
\Class{BatchReactor} was configured to run with a 3 batch core on 18 month cycles and
a 2-month refueling period.  Adjusting and setting parameters such as these is
as simple as editing numbers in an input file such as:

@@

Figure \ref{fig:puseries1} shows the full-system plutonium buildup for open
(no recycle), modified open, and closed (infinite-pass recycle) \TODO{whats
the diff btw closed and the multi-pass from above? It's referred to as fully
closed multi-pass recycle, which is a bit confusing.} variations of
the scenario described above (all just a single reactor).  The figure was
generated directly from \Cyclus output data. After several batch cycles (near
month 300) in the modified open and closed cases, enough separated fissile
material accumulates in the fuel fabrication facility to generate a full
recycled batch.  When this batch is transmuted, more plutonium is burned than
created.  This results in a drop in the total fuel cycle system plutonium
inventory.  This pattern repeats roughly every 10 cycles (200 months) for the
modified open case and every 9 cycles (180 months) for the closed case.
Because the modified open scenario does not re-recycle material, it takes the
fabrication facility 1 cycle longer to accumulate a full batch of
fissile material.
